Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-05-09 Ben_Manuscripts/structure_paper/Draft.tex
edits for the day

\makeatletter
\newcommand*{\addFileDependency}[1]{% argument=file name and extension
  \typeout{(#1)}
  \@addtofilelist{#1}
  \IfFileExists{#1}{}{\typeout{No file #1.}}
}
\makeatother

\newcommand*{\myexternaldocument}[1]{%
    \externaldocument{#1}%
    \addFileDependency{#1.tex}%
    \addFileDependency{#1.aux}%
}

\externaldocument[S-]{supplemental}

@@

  % BJC5: trying things out with 'columns per pore' instead of 'monomers per layer'.
  Our simulations best support a model built with 5 monomer columns per pore based on
  the measured equilibrated pore-to-pore distances. To discern the composition of
  the monomer layers, addressing question (\ref{point:monomernum}), we ran
  simulations of systems created with 4--8 columns per pore. We built systems in both
  %BJC5: need to make parallel displaced and sandwiched configurations clear in methods
  the parallel displaced and sandwiched configurations and equilibrated them according
  to the dry equilibration procedure. We test all systems with an initial vertical monomer 
  spacing, \textit{d}, of 3.7~\AA in accordance with R-$\pi$. We tested 4 additional systems with
  monomers initially spaced 5 \AA~apart vertically (See supporting info for more details on       
  %BJC5: integrate supplemental section labels into main paper.
  sensitivity to initial layer spacing). The pore-to-pore spacing is equilibrated, as defined in
  section~\ref{method:equil_time} in all systems after 400 ns of simulation.
  Figure~\ref{fig:p2p} shows the equilibrated pore-to-pore distances for all systems tested. 
  Systems built with 5 columns in each pore equilibrate to a pore spacing that is most
  %BJC5: New paragraph? 
  consistent with the experimental value of 4.12 nm derived from SAXS measurements 
  (Figure~\ref{fig:SAXS}).
  %BJC5: comment about disordered systems

  The remainder of this discussion will focus on the analysis of systems built with
  5 columns per pore. Systems built with 6 columns per pore have an equilibrated
  pore spacing c.a. 0.50 nm higher than experiment. Systems built with 4 columns per pore
  %BJC5: edit above with consciencenous of new 6 mon/layer sim data
  equilibrate to a pore spacing 0.25 nm lower than experiment. All systems tested are at least
  metastable on the timescales studied here, however not all make physical sense or
  fit the experimental profile that we are trying to match. In the limit of infinite simulation
  time, all simulations will converge to a single density. It is our intention to choose an
  initial configuration which quickly reaches a monomer density close to experiment. We believe
  systems built with 5 columns per pore achieve this goal.

  \begin{figure}
	\centering
	\includegraphics[width=\linewidth]{p2p.png}
	\caption{Systems with 5 columns per pore have equilibrated pore spacings closest to
			 the experimental value of 4.12 nm. The equilibrated pore spacing of the model 	
			 increases as the number of columns in each pore increases. The pore spacing
			 of systems starting in the sandwiched configuration are systematically lower
			 %BJC5: double check this statement once all data is present
			 than those started in the parallel displaced configuration.}~\label{fig:p2p}
  \end{figure}

@@

  The simulated XRD patterns show moderate qualitative agreement with experiment. R-alkanes and
  R-pores appear in the expected location. R-pores is more intense than experiment, likely
  because we are simulating a perfect, infinite hexagonal array. The real system has defects and
  domain misalignment which decreases the overall intensity.
  % MRS4: comments from Matt suggest that domain misaligment shouldn't alone be responsible for 
  % the difference in intensity ratio. Some of the experiments should help explain it better. 	
  % Let's talk!
  % BJC4: So a combo of: domain misalignment, defects, slow dynamics of simulated system, only 4 
  % pores in unit cell, tortuosity (?)
  % MRS5: maybe, there's a question of how we can demonstrate the magnitude of any of these 
  % effects.
  R-spots appears to be weaker in the simulated patterns. They are also partially engulfed by
  the wide R-$\pi$ reflection. We further explore R-spots in Section~\ref{section:rspots}.  
  R-$\pi$ appears at a lower $q_z$ value than experiment. In all systems, the reflection 
  reaches its maximum at $q_z < 1.5 \AA^{-1}$ which means that monomers prefer to stack 
  at least 4.2 \AA~apart rather than 3.7 \AA. This behavior is not surprising since GAFF models
  atoms as point charges and does not appropriately model the aromatic $\pi-\pi$ interactions 
  which would cause the monomers to stack closer together. We will explore R-$\pi$ in more detail
  in Section~\ref{section:rpi}. R-double does not appear in any of the patterns. We will explore
  its possible origins and reasons that it does not appear in our simulated patterns in
  Section~\ref{section:rdouble}.

  The simulated XRD pattern of the parallel displaced configuration shows an additional
  reflection due to its helical structure. There are horizontal reflections near $|q_z|= 
  0.7~\AA^{-1}$, half of the $q_z$ value of R-$\pi$. The reflection does not cross through
  $q_r = 0~\AA^{-1}$ so it does not appear for the same reason as R-double. This type of pattern
  is characteristic of a helix (reference something).
  %BJC5: reference something like a dna diffraction paper
  It is possible that these reflections contribute to the continuation of R-double into R-
  alkanes, as seen in the experimental pattern.

  %BJC4: This paragraph might fit better before qualitative description
  %BJC5: This could potentially supplement parts of the qualitative descriptions.
  We quantified the numerical discrepancies present when comparing the relative intensities
  of each reflection of interest between experimental and simulated patterns. Table 
  ~\ref{table:relative_inensities_300K} quantifies the relative intensity of each reflection for 
  all systems tested. The patterns are normalized so that the average intensity of R-alkanes 
  equals 1.
  % BJC5: above is stated in methods. Not sure if it needs to be restated.  
  % BJC5: I need to explain how I calculated these intensities somewhere. Is this the right
  % place to do it? I think it would just be confusing in the methods. I could also move it
  % to supplemental.
  % BJC5: Definitely need demonstrative figures in supporting info.
  We measured the approximate intensity of R-$\pi$ by measuring the intensity of the peak shown
  by the cross-section of the 2D pattern at $q_r=0$. The relative intensity of R-$\pi$ is 
  significantly higher than experiment in our simulations. R-spots is measured as the average
  intensity within the region bounded by a 'spot'. Spots are identified based on visual 
  inspection. If the spots were not easily discernable, then the intensity was taken as that of
  the intersection of R-alkanes at half the $q_z$ value of R-$\pi$, since that is where it 
  appears experimentally. The intensity of R-spots is slightly lower than experiment in all 
  cases. There is no R-double intensity to be measured.

  \begin{table}[h]
  \centering
  \begin{tabular}{cccccc}
  \toprule
 		   & \multicolumn{5}{c}{Configuration} \\
  \hline
  Reflection & Experiment & Sandwiched & Parallel Displaced & Disordered Sandwiched & Disordered Parallel Displaced \\
  \midrule
  R-alkanes & 1.0 &  1.0 &  1.0 & 1.0 & 1.0  \\  
  R-spots   & 1.3 &  1.2 &  1.2 & 1.2 & 1.2  \\
  R-$\pi$   & 2.8 & 18.1 & 14.2 & 7.8 & 10.0 \\
  R-double  & 0.9 &  --  & --   &  -- & --   \\ 
  \bottomrule
  \end{tabular}
  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
  than experiment and R-spots reflections that are slightly lower than experiment. R-double
  does not appear in any patterns, and thus has no measurable intensity.}
  \label{table:relative_inensities_300K} 
  \end{table}

@@

%MRS5: put a little more of the rational for looking at this here. Why should they care?
  We plotted the number densities of heavy atoms in the head group, carbon atoms in the tail
  region and all sodium ions (Figure~\ref{fig:densities}). For the head group
  region, we used the carbon atoms making up the aromatic ring. For the tail
  region we used only carbon atoms of the monomer tails (See Supporting
  Information for diagram). We average the histograms over at least 50 ns of
  equilibrated trajectory.

>>>>

\SectionNumbersOn

%\makeatletter
%\newcommand*{\addFileDependency}[1]{% argument=file name and extension
%  \typeout{(#1)}
%  \@addtofilelist{#1}
%  \IfFileExists{#1}{}{\typeout{No file #1.}}
%}
%\makeatother
% 
%\newcommand*{\myexternaldocument}[1]{%
%    \externaldocument{#1}%
%    \addFileDependency{#1.tex}%
%    \addFileDependency{#1.aux}%
%}

\externaldocument[S-]{supporting_information}

@@

  % BJC5: trying things out with 'columns per pore' instead of 'monomers per layer'.
  Our simulations best support a model built with 5 monomer columns per pore based on
  the measured equilibrated pore-to-pore distances. To discern the composition of
  the monomer layers, addressing question (\ref{point:monomernum}), we ran
  simulations of systems created with 4--8 columns per pore. We built systems in both
  the parallel displaced and sandwiched configurations and equilibrated them according
  to the dry equilibration procedure. We tested all systems with an initial vertical monomer 
  spacing, \textit{d}, of 3.7 \AA~in accordance with R-$\pi$. We tested 4 additional systems with
  monomers initially spaced 5 \AA~apart vertically (See section~\ref{S-section:initial_pore_spacing}
  of the supporting info for more details on sensitivity to initial layer spacing). 
  The pore-to-pore spacing is equilibrated, as defined in section~\ref{method:equil_time},
  % BJC5: this achemso format does not have section numbers so I can't reference sections
  % within this document.
  in all systems after 400 ns of simulation. Figure~\ref{fig:p2p} shows the equilibrated
  pore-to-pore distances for all systems tested.

  Systems built with 5 columns in each pore equilibrate to a pore spacing that is most 
  consistent with the experimental value of 4.12 nm derived from SAXS measurements 
  (Figure~\ref{fig:SAXS}). The remainder of this discussion will focus on the analysis of
  systems built with 5 columns per pore. Systems built with 6 columns per pore, and 
  $\mathit{d}=3.7~\AA~$, have an equilibrated pore spacing c.a. 0.50 nm higher than experiment.
  Systems built with 4 columns per pore equilibrate to an average pore spacing 0.25 nm lower
  than experiment.

  %BJC5: thesis needs rewording.
  Systems built with 6 columns-per-pore and $\mathit{d}=5~\AA~$ are not compact
  in the z-direction. The final pore spacing is close to experiment within its uncertainty.
  Relative to 6 column-per-pore systems started with $\textit{d}=3.7~\AA~$, the unit cell
  is elongated in its z dimension and contracted in its x and y dimensions, however the
  box volume stays nearly constant in all cases (Figure~\ref{fig:box_dimensions}). The system
  is likely not fully equilibrated and may eventually rearrange into something that resembles
  a 5 column-per-pore system. Further investigations into this are beyond the scope of this
  paper.

  \begin{figure}[htb]
  \centering
  \includegraphics[width=\textwidth]{box_dimensions.png}
  \caption{When monomers are initially stacked 5 \AA~apart ($\textit{d}=5 \AA~$), the unit cell
  expands in the z direction and contracts in its x and y dimensions. The volume remain nearly
  constant across all cases. The y dimension box vectors are not included since we use 
  semiisotropic pressure coupling which requires that the x and y box vectors change uniformly.}\label{fig:box_dimensions}
  \end{figure}

  All systems tested are at least metastable on the timescales studied here, however not all 
  make physical sense or fit the experimental profile that we are trying to match. In the limit
  of infinite simulation time, all simulations will converge to a single density. It is our 
  intention to choose an initial configuration which quickly reaches a monomer density close 
  to experiment. We believe systems built with 5 columns per pore achieve this goal.

  \begin{figure}
	\centering
	\includegraphics[width=\linewidth]{p2p.png}
	\caption{Systems with 5 columns per pore have equilibrated pore spacings closest to
			 the experimental value of 4.12 nm. The equilibrated pore spacing of the model 	
			 increases as the number of columns in each pore increases.}~\label{fig:p2p}
  \end{figure}

@@

  The simulated XRD patterns show moderate qualitative agreement with experiment. R-alkanes and
  R-pores appear in the expected location. R-pores is more intense than experiment, likely
  because we are simulating a near perfect, infinite hexagonal array. The real system has 
  defects and domain misalignment which decreases the overall intensity.
  % MRS4: comments from Matt suggest that domain misaligment shouldn't alone be responsible for 
  % the difference in intensity ratio. Some of the experiments should help explain it better. 	
  % Let's talk!
  % BJC4: So a combo of: domain misalignment, defects, slow dynamics of simulated system, only 4 
  % pores in unit cell, tortuosity (?)
  % MRS5: maybe, there's a question of how we can demonstrate the magnitude of any of these 
  % effects.
  R-spots appears to be weaker in the simulated patterns. They are also partially engulfed by
  the wide R-$\pi$ reflection. R-$\pi$ appears at a lower $q_z$ value than experiment. In all
  systems, the reflection reaches its maximum at $q_z < 1.5 \AA^{-1}$ which means that monomers 
  prefer to stack at least 4.2 \AA~apart rather than 3.7 \AA. This behavior is not surprising 
  since GAFF models atoms as point charges and does not appropriately model the aromatic
  $\pi-\pi$ interactions which would cause the monomers to stack closer together. R-double 
  does not appear in any of the patterns.

%  We will explore its possible origins and reasons
%  that it does not appear in our simulated patterns in Section~\ref{section:rdouble}.

  The simulated XRD pattern of the parallel displaced configuration shows an additional
  reflection due to its helical structure. There are horizontal reflections near $|q_z|= 
  0.7~\AA^{-1}$, half of the $q_z$ value of R-$\pi$. The reflection does not cross through
  $q_r = 0~\AA^{-1}$ so it does not appear for the same reason as R-double. This type of pattern
  is characteristic of a helix (reference something).
  %BJC5: reference something like a dna diffraction paper
  It is possible that these reflections contribute to the continuation of R-double into R-
  alkanes, as seen in the experimental pattern.
  %BJC5: not sure above sentence is clear (or necessary to say)

  We quantified the numerical discrepancies present when comparing the relative intensities
  of each reflection of interest between experimental and simulated patterns. Table 
  ~\ref{table:relative_inensities_300K} quantifies the relative intensity of each reflection for 
  all systems tested. The patterns are normalized so that the average intensity of R-alkanes 
  must equal 1.
  % BJC5: show how intensities are measured in supporting info
  We measured the approximate intensity of R-$\pi$ by measuring the intensity of the peak shown
  by the cross-section of the 2D pattern at $q_r=0$. The relative intensity of R-$\pi$ is 
  significantly higher than experiment in our simulations. R-spots is measured as the average
  intensity within the region bounded by a 'spot'. Spots are identified based on visual 
  inspection. If the spots were not easily discernable, then the intensity was taken as that of
  the intersection of R-alkanes at half the $q_z$ value of R-$\pi$, since that is where it 
  appears experimentally. The intensity of R-spots is slightly lower than experiment in all 
  cases. There is no R-double intensity to be measured. Descriptive figures are provided in the
  supporting information to make these measurements clear.

  \begin{table}[h]
  \centering
  \begin{tabular}{cccccc}
  \toprule
 		   & \multicolumn{5}{c}{Configuration} \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes & 1.0 &  1.0 &  1.0 & 1.0 & 1.0  \\  
  R-spots   & 1.3 &  1.2 &  1.2 & 1.2 & 1.2  \\
  R-$\pi$   & 2.8 & 18.1 & 14.2 & 7.8 & 10.0 \\
  R-double  & 0.9 &  --  & --   &  -- & --   \\ 
  \bottomrule
  \end{tabular}
  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
  than experiment and R-spots reflections that are slightly lower than experiment. R-double
  does not appear in any patterns, and thus has no measurable intensity.}
  \label{table:relative_inensities_300K} 
  \end{table}

@@

%MRS5: put a little more of the rational for looking at this here. Why should they care?
  We are most interested in the pore architecture. What's happening in the tails is unimportant.

  We plotted the number densities of heavy atoms in the head group, carbon atoms in the tail
  region and all sodium ions (Figure~\ref{fig:densities}). For the head group
  region, we used the carbon atoms making up the aromatic ring. For the tail
  region we used only carbon atoms of the monomer tails (See Supporting
  Information for diagram). We average the histograms over at least 50 ns of
  equilibrated trajectory.
